---
title: "Presentations"
subtitle: "SDSS 2023: Reproducible Documents, Websites,<br>and Books with Quarto"
institute: "Duke University + Posit"
author: "Dr. Mine Çetinkaya-Rundel"
date: "2023-05-23"
footer: "[🔗 mine.quarto.pub/quarto-sdss](https://mine.quarto.pub/quarto-sdss)"
logo: "../images/logo.png"
format:
  revealjs:
    theme: ../style/slides.scss
    transition: fade
    slide-number: true
    chalkboard: true
editor: visual
execute:
  freeze: auto
  echo: true
---

```{r}
#| label: setup
#| include: false

# set width of code output
options(width = 65)

# load background packages
library(countdown)
```

# Anatomy of a Quarto presentation

## Components

1.  Metadata: YAML

2.  Text: Markdown

3.  Code: Executed via `knitr` or `jupyter`

. . .

**Weave it all together**, and you have a beautiful, functional slide deck!

## Our turn {.smaller}

::: task
Let's build a presentation together from `hello-penguins-slides.qmd` and showcase the following features of Quarto presentations:

-   Hierarchy, headers, and document outline

-   Incremental lists

-   Columns and tabsets

-   Code, output location, code highlighting

-   Logo and footer

-   Making things fit on a slide

-   Chalkboard

-   Multiplex

-   Publishing your presentation to Quarto Pub
:::

## Your turn

::: task
Pick up where we left off and

-   Change the [transition style](https://quarto.org/docs/presentations/revealjs/advanced.html#slide-transitions) between slides

-   Change the [slide size](https://quarto.org/docs/presentations/revealjs/advanced.html#presentation-size)

-   Add [slide numbers](https://quarto.org/docs/presentations/revealjs/presenting.html#slide-numbers)
:::

```{r}
#| echo: false

countdown(minutes = 15)
```

## Our turn

::: task
Let's continue building our a presentation together from `hello-penguins-slides.qmd` and showcase the following features of Quarto presentations:

-   Fragments

-   Title slide attributes

-   Speaker notes
:::

# Wrap up

## Quarto presentation formats

-   [`revealjs`](https://quarto.org/docs/presentations/revealjs) for HTML slides

    -   Essentially the replacement for `xaringan`, but with Pandoc-native syntax

-   [`beamer`](https://quarto.org/docs/presentations/beamer.html) for LaTeX slides

-   [PowerPoint](https://quarto.org/docs/presentations/powerpoint.html) for when you *have to* collaborate via MS Office

## Learn more

::: learn-more
[quarto.org/docs/presentations](https://quarto.org/docs/presentations)

```{=html}
<iframe src="https://quarto.org/docs/presentations/" width="100%" height="500" style="border:2px solid #123233;" title="Quarto Presentations"></iframe>
```
:::

## Questions

::: task
Any questions / anything you'd like to review before we wrap up this module?
:::
