---
title: "Websites"
subtitle: "SDSS 2023: Reproducible Documents, Websites,<br>and Books with Quarto"
institute: "Duke University + Posit"
author: "Dr. Mine Çetinkaya-Rundel"
date: "2023-05-23"
footer: "[🔗 mine.quarto.pub/quarto-sdss](https://mine.quarto.pub/quarto-sdss)"
logo: "../images/logo.png"
format:
  revealjs:
    theme: ../style/slides.scss
    transition: fade
    slide-number: true
    chalkboard: true
editor: visual
execute:
  freeze: auto
  echo: true
---

```{r}
#| label: setup
#| include: false

# set width of code output
options(width = 65)

# load background packages
library(countdown)
```

# Anatomy of a Quarto project

## Quarto projects

-   Quarto projects have a `_quarto.yml` file

-   The `type` field in this file indicates the type of project:

    -   `default`: Collection of documents

    -   `website`: Websites (and blogs)

    -   `books`: Books 😃

## Quarto websites

-   Websites are essentially `format: html` + a Quarto Project

-   But a website is different than `format: html` in that it has multiple pages

-   Websites are our first exploration into Quarto Projects

-   Websites and books are very similar in that they associate multiple pages/resources into a connected resource

## Our turn

::: task
Let's build a website together from all of the documents we've created so far and highlight the following features of Quarto websites:

-   `_quarto.yml`

-   `index.qmd` / landing page / change landing page

-   Navigation

-   Freeze

-   Themes and dark theme toggle

-   Publishing to QuartoPub

-   An aspect of the workshop webpage that you fancy?
:::

## Your turn

::: task
Pick up where we left off and

-   Add an [about page](https://quarto.org/docs/websites/website-about.html).
-   Cross reference one page from another.
:::

```{r}
#| echo: false

countdown(minutes = 15)
```

## Our turn

::: task
Let's now add a blog component to our website.

-   Add a folder called `posts` and create a few minimal blog post entries and collect these from a blog page using the [listings feature](https://quarto.org/docs/websites/website-listings.html).

-   Change the style of listings.
:::

# Computations

## When should code be re-run? {.smaller}

::: incremental
-   You might have a reason to re-run all code in a Quarto website (every single chunk in every single document) every time you render the website.

-   But, chances are, that's not what you want.

    -   Just playing around styling -- you probably don't want to run the code again

    -   Changed some code in a document -- you probably want to re-run the code in that document, but not necessarily others

    -   Made a big change affecting computations on many or all pages -- you probably want to re-run all code

-   `freeze` and `cache` options give you fine control over these decisions
:::

## Freeze {.smaller}

-   The `freeze` option controls when/if computational documents be re-rendered during a global project render:

``` yaml
execute:
  freeze: true  # never re-render during project render
```

``` yaml
execute:
  freeze: auto  # re-render only when source changes
```

``` yaml
execute:
  freeze: false  # always re-render
```

-   The `freeze` option is typically added to a `_metadata.yml` file within a specific directory, affecting all files in that directory.

-   For blogs, set `feeze` in `_metadata.yml` at the root of the `posts` directory.

-   You can have it only within specific subdirectories for more complex sites.

## Cache

-   Cache stores the results of computations for a specific file.

-   Cache invalidation is triggered by changes in chunk source code (or other cache attributes you've defined).

-   `cache` can also be set at the chunk level. Consider using the cache for computationally expensive chunks.

## Freeze vs. cache {.smaller}

-   Freeze option is typically set

    -   for the whole website in `_quarto.yml`, or

    -   for files within a directory in `_metadata.yml` in that directory

``` yaml
execute: 
  freeze: auto
```

-   Cache option is typically set for a given file or for individual chunk(s) in a file.

``` yaml
execute:
  cache: true
```

or

```{r}
#| echo: fenced
#| cache: true

1 + 1
```

# Publishing

## QuartoPub

- [Quarto Pub](https://quartopub.com/) is a free publishing service for content created with Quarto. It is ideal for blogs, course or project websites, books, presentations, and personal hobby sites.

- Publish with `quarto publish`:

``` {.bash filename="Terminal"}
quarto publish quarto-pub
```

- Gain a `_publish.yml` that is safe to check into version control.

## Other venues

- GitHub Pages
- Posit Connect
- Netlify
- Confluence
- [More venues](https://quarto.org/docs/publishing/other.html)

# Wrap up

## Questions

::: task
Any questions / anything you'd like to review before we wrap up this module?
:::
