---
title: "Manuscripts"
subtitle: "SDSS 2023: Reproducible Documents, Websites,<br>and Books with Quarto"
institute: "Duke University + Posit"
author: "Dr. Mine Çetinkaya-Rundel"
date: "2023-05-23"
footer: "[🔗 mine.quarto.pub/quarto-sdss](https://mine.quarto.pub/quarto-sdss)"
logo: "../images/logo.png"
format:
  revealjs:
    theme: ../style/slides.scss
    transition: fade
    slide-number: true
    chalkboard: true
editor: visual
execute:
  freeze: auto
  echo: true
---

```{r}
#| label: setup
#| include: false

# set width of code output
options(width = 65)

# load background packages
library(countdown)
```

# Anatomy of a Quarto journal article

## Components

1.  Metadata: YAML

2.  Text: Markdown

3.  Code: Executed via `knitr` or `jupyter`

. . .

**Weave it all together**, and you have a beautiful, reproducible journal article!

## Our turn

::: task
Let's build a manuscript together from for JASA and showcase the following features of Quarto journal articles:

-   PDF output

-   YAML

-   Citations
:::

## Your turn

::: task
Pick up where we left off and

-   Add co-authors

-   Add another citation from a DOI

-   Add an appendix
:::

```{r}
#| echo: false

countdown(minutes = 10)
```

# Wrap up

## Quarto journal articles

::: callout-caution
## TO DO

Add links to learn more here
:::

## Questions

::: task
Any questions / anything you'd like to review or learn before we wrap up the workshop?
:::
