---
title: "Books"
subtitle: "SDSS 2023: Reproducible Documents, Websites,<br>and Books with Quarto"
institute: "Duke University + Posit"
author: "Dr. Mine Çetinkaya-Rundel"
date: "2023-05-23"
footer: "[🔗 mine.quarto.pub/quarto-sdss](https://mine.quarto.pub/quarto-sdss)"
logo: "../images/logo.png"
format:
  revealjs:
    theme: ../style/slides.scss
    transition: fade
    slide-number: true
    chalkboard: true
editor: visual
execute:
  freeze: auto
  echo: true
---

```{r}
#| label: setup
#| include: false

# set width of code output
options(width = 65)

# load background packages
library(countdown)
```

# Anatomy of a Quarto book

## Quarto books

-   Books are also essentially `format: html` + a Quarto Project

-   But a book is different than `format: html` in that it has multiple pages

-   Books and websites are very similar in that they associate multiple pages/resources into a connected resource

-   Books and websites are different in how they treat components: pages vs. cross-referencable chapters for website and books, respectively

## Our turn

::: task
Let's build a book together from all of the documents we've created so far and highlight the following features of Quarto websites:

-   `_quarto.yml`

-   `index.qmd` / landing page / change landing page

-   Callouts

-   Cross references

-   Unnumbered chapters

-   Sections

-   Appendices
:::

## Your turn

::: task
Pick up where we left off and

-   Give a title to your book.
-   Add a numbered figure and cross-reference it.
-   Add a numbered figure to another chapter, cross-reference it, and observe the numbering scheme
:::

```{r}
#| echo: false

countdown(minutes = 15)
```

# Publishing

## QuartoPub

-   [Quarto Pub](https://quartopub.com/) is a free publishing service for content created with Quarto. It is ideal for blogs, course or project websites, books, presentations, and personal hobby sites.

-   Publish with `quarto publish`:

``` {.bash filename="Terminal"}
quarto publish quarto-pub
```

-   Gain a `_publish.yml` that is safe to check into version control.

## Other venues

-   GitHub Pages
-   Posit Connect
-   Netlify
-   Confluence
-   [More venues](https://quarto.org/docs/publishing/other.html)

# Wrap up

## Computations

Same `freeze` and `cache` ideas for websites apply to books.

## Publishing

Same publishing options for websites apply to books as well.

## Learn more

::: learn-more
[quarto.org/docs/books](https://quarto.org/docs/books/)

```{=html}
<iframe src="https://quarto.org/docs/books" width="100%" height="500" style="border:2px solid #123233;" title="Quarto Journal Articles"></iframe>
```
:::

## Questions

::: task
Any questions / anything you'd like to review before we wrap up this module?
:::

