---
title: "Miscellaneous"
subtitle: "SDSS 2023: Reproducible Documents, Websites,<br>and Books with Quarto"
institute: "Duke University + Posit"
author: "Dr. Mine Çetinkaya-Rundel"
date: "2023-05-23"
footer: "[🔗 mine.quarto.pub/quarto-sdss](https://mine.quarto.pub/quarto-sdss)"
logo: "../images/logo.png"
format:
  revealjs:
    theme: ../style/slides.scss
    transition: fade
    slide-number: true
    chalkboard: true
editor: visual
execute:
  freeze: auto
  echo: true
---

```{r}
#| label: setup
#| include: false

# set width of code output
options(width = 65)

# load background packages
library(countdown)
```

# Tools

## Logos

Places the logo on top of the sidebar and a small version in the browser tab.

``` yaml
website:
  sidebar:
    logo: "images/logo.png"
  favicon: "images/logo.png"
```

## Icons

``` yaml
website:
  sidebar:
    logo: "images/logo.png"
    tools:
      - icon: github
        href: https://github.com/quart-cli
        text: "GitHub organization"
      - icon: code-square
        href: https://posit.cloud
        text: "Posit Cloud"
```

## Socials

Some examples include:

-   [Twitter Cards](https://developer.twitter.com/en/docs/twitter-for-websites/cards/overview/abouts-cards) provide an enhanced appearance when someone links to your site on Twitter.

-   The [Open Graph protocol](#0) enables richer sharing of links to articles on the web, e.g., with preview images.

``` yaml
website:
  twitter-card: true
  open-graph: true
```

## Learn more

::: learn-more
[quarto.org/docs/websites/website-tools.html](https://quarto.org/docs/websites/website-tools.html)

```{=html}
<iframe src="https://quarto.org/docs/websites/website-tools.html" width="100%" height="500" style="border:2px solid #123233;" title="Quarto Journal Articles"></iframe>
```
:::

## Your turn

::: task
Pick up where we left off and

-   Add a link to a GitHub repository with a [bootstrap icon](https://icons.getbootstrap.com/).
-   Review <https://quarto.org/docs/websites/website-tools.html> and implement one new tool we haven't introduced.
:::

```{r}
#| echo: false

countdown(minutes = 10)
```

# Theming

## Theme options

-   One of 25 [Bootswatch](https://bootswatch.com/) themes

-   Custom themes

-   A combination of the two

## Setting the theme

In `_quarto.yml`:

``` yaml
format:
  html:
    theme: default
```

## Dark mode

Setting a light and dark theme makes both available with a toggle automatically added to your website:

``` yaml
format:
  html:
    theme:
      light: flatly
      dark: darkly
```

## Customizing themes

To customize a theme, add a custom `.scss` file that is then called in `_quarto.yml`, e.g.:

``` yaml
format:
  html:
    theme:
      light: [flatly, custom.scss]
      dark: darkly
```

## SCSS files

SCSS files have the following form:

``` scss
/*-- scss:defaults --*/
$h2-font-size:          1.6rem !default;
$headings-font-weight:  500 !default;
$body-color:            $gray-700 !default;

/*-- scss:rules --*/
h1, h2, h3, h4, h5, h6 {
  text-shadow: -1px -1px 0 rgba(0, 0, 0, .3);
}
```

-   The `defaults` section is where you list variables

-   The `rules` section is where you list (CSS) rules

## SASS variables

-   Some examples include:

    -   `$body-bg`: The page background color.

    -   `$link-color`: The link color.

    -   `$font-family-monospace`: The monospace font family for the page.

    -   `$callout-color-<type>`: The colors for the various types of callouts.

-   See the full list at <https://quarto.org/docs/output-formats/html-themes.html#sass-variables>.

## Learn more

::: learn-more
[quarto.org/docs/output-formats/html-themes.html](https://quarto.org/docs/output-formats/html-themes.html)

```{=html}
<iframe src="https://quarto.org/docs/output-formats/html-themes.html" width="100%" height="500" style="border:2px solid #123233;" title="Quarto Journal Articles"></iframe>
```
:::

## Tip

::: callout-tip
## Figuring out what to style

-   Use your browser's developer tools.

-   Refer to the [default values for SASS variables](https://github.com/twbs/bootstrap/blob/main/scss/_variables.scss) and set to something absurd (red and bold or giant size) while testing. Once you have the correct variable or rule identified, set the style values to what you want them to be.
:::

## Your turn

::: task
Pick up where we left off and

-   Change the theme of your project to one of the Bootswatch themes.
-   Add light / dark mode toggle, experimenting with different light and dark themes.
-   Stretch goal: Customize 1-2 elements of your theme.
:::

```{r}
#| echo: false

countdown(minutes = 10)
```

# Request hour

## Your turn

to request!

::: .task
What other aspects / features of a Quarto website or book would you like to learn about?
:::

